Capstone Movielens Report

### 2025-12-26 reports/capstone-movielens.site/02.4.UE-model.Rmd

Now, we are ready to compute the *Mean Squared Errors (MSEs)* for the samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function (described in the [Utility Functions] section of [Appendix A](#appndx_a)).

@@

::: {.noteblock data-latex=""}
In the code snippet above, we use the user-defined function [mse](#func.mse) described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
:::

>>>>

Now, we are ready to compute the *Mean Squared Errors (MSEs)* for the samples used in _K-Fold Cross-Validation_ (additionally using the [clamp](#func.clamp) helper function described in the [Common Helper Functions]/[Utility Functions] section of [Appendix A](#appndx_a)).

@@

::: {.noteblock data-latex=""}
In the code snippet above, we also use the user-defined function [mse](#func.mse) described in the [Common Helper Functions]/[(Root) Mean Squared Error Calculation] section of [Appendix A](#appndx_a).
:::

### 2025-12-26 reports/capstone-movielens.site/02.5.UME-model.Rmd
Report sections review: the model tuning & regularization.

We can now construct predictors and see how much the `RMSE` improves[@IDS2_24-1_ME].

@@

Now, let's visualize the results of the $\lambda$ range pre-configuration:
``` {r  main-script@l}
cv.UME.preset.result$tuned.result |>
  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = TeX(r'[$\lambda$]'), 
              ylabel = "RMSE")
```

>>>>

We can now construct predictors and see how much the *RMSE* score improves[@IDS2_24-1_ME].

@@

Now, let's visualize the results of the $\lambda$ range pre-configuration using the following [code snippet]((https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L596):
``` {r  main-script@l}
cv.UME.preset.result$tuned.result |>
  data.plot(title = TeX(r'[UME Model Regularization: $\lambda$ Range Pre-configuration]'),
              xname = "parameter.value", 
              yname = "RMSE", 
              xlabel = TeX(r'[$\lambda$]'), 
              ylabel = "RMSE")
```
